func_tmp

### 2025-12-30 reports/capstone-movielens.site/work/draft-snippert.Rmd
Report section review (completed): UMGYDE Model: Matrix Factorization (MF).

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [@fn](#func.@fn) described in the [sec_name] section of [Appendix A: Support Functions].
:::

@@

>>>>

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [@fn](#func.@fn) described in the [sec_name] section of [Appendix A: Support Functions].
:::
### MF: Helper Functions

#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) Function {#func.mf.residual.dataframe}
\

::: { #func.mf.residual.dataframe.args.description .sidebar }
##### Description
\

Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section.

##### Arguments
\

###### ***train_set***
\

::: { #func.mf.residual.dataframe.args.train_set .sidebar }
The dataset to be trained.
:::

##### Source Code
\

The folowing is the source code of the function:
```{r eval=FALSE}
mf.residual.dataframe <- function(train_set){
  train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(rglr.UMGY_effect, by='year') |>
    left_join(rglr.UMGYD_effect, by='days') |>
    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
    select(userId, movieId, rsdl)
}
```

::: {.noteblock data-latex=""}
The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) script on _GitHub_.
:::

##### Return
\

A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.args.description) above for the details).

#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
\

This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.

##### Arguments
\

::: { #func.UMGYDE_model.predict.args.test_set .sidebar }
###### ***test_set***
\

The dataset for testing the _UMGYDE Model_ after it has been fully trained.
:::

##### Source Code
\

The following is the source code of the function:
```{r eval=FALSE}
UMGYDE_model.predict <- function(test_set) {
  test_set |>
    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
}
```

::: {.noteblock data-latex=""}
The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) script on _GitHub_.
:::

##### Return
\

A data frame object containing predicted values.

@@

### MF: Helper Functions

#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) Function {#func.mf.residual.dataframe}
\

::: { #func.mf.residual.dataframe.args.description .sidebar }
##### Description
\

Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section.

##### Arguments
\

###### ***train_set***
\

::: { #func.mf.residual.dataframe.args.train_set .sidebar }
The dataset to be trained.
:::

##### Source Code
\

The folowing is the source code of the function:
```{r eval=FALSE}
mf.residual.dataframe <- function(train_set){
  train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(rglr.UMGY_effect, by='year') |>
    left_join(rglr.UMGYD_effect, by='days') |>
    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
    select(userId, movieId, rsdl)
}
```

::: {.noteblock data-latex=""}
The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) script on _GitHub_.
:::

##### Return
\

A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.args.description) above for the details).

#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
\

This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.

##### Arguments
\

::: { #func.UMGYDE_model.predict.args.test_set .sidebar }
###### ***test_set***
\

The dataset for testing the _UMGYDE Model_ after it has been fully trained.
:::

##### Source Code
\

The following is the source code of the function:
```{r eval=FALSE}
UMGYDE_model.predict <- function(test_set) {
  test_set |>
    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
}
```

::: {.noteblock data-latex=""}
The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) script on _GitHub_.
:::

##### Return
\

A data frame object containing predicted values.

### 2025-12-30 reports/capstone-movielens.site/work/func-descr.template.Rmd
Report section review (completed): UMGYDE Model: Matrix Factorization (MF).

>>>>

#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
\

::: { #func.UMGYDE_model.predict.usage .sidebar }
##### Usage
\

::: { #func.UMGYDE_model.predict.args .sidebar }
##### Arguments
\

::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
  - **test_set:** ;

::: { #func.UMGYDE_model.predict.details .sidebar }
##### Details
\

::: { #func.UMGYDE_model.predict.value .sidebar }
##### Value
\

::: { #func.UMGYDE_model.predict.code .sidebar }
##### Source Code
\

The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
```{r eval=FALSE}
UMGYDE_model.predict <- function(test_set) {
  test_set |>
    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
}
```

::: {.noteblock data-latex=""}
The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
:::
:::

### 2025-12-30 reports/capstone-movielens.site/work/tmp/func_tmp.Rmd
Report section review (completed): UMGYDE Model: Matrix Factorization (MF).

>>>>

#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
\

::: { #func.UMGYDE_model.predict.usage .sidebar }
##### Usage
\

```{r eval=FALSE}

```
:::

::: { #func.UMGYDE_model.predict.args .sidebar }
##### Arguments
\

::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
  - **test_set:** ;

:::
:::

::: { #func.UMGYDE_model.predict.details .sidebar }
##### Details
\

::: { #func.UMGYDE_model.predict.value .sidebar }
##### Value
\

::: { #func.UMGYDE_model.predict.code .sidebar }
##### Source Code
\

The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
```{r eval=FALSE}
UMGYDE_model.predict <- function(test_set) {
  test_set |>
    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
}
```

::: {.noteblock data-latex=""}
The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
:::
:::
